### 2018-08-22 Sections/acknowledgements.tex
Economics update
Redid economics
acks

We acknowledge Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Jonathan Olson \& Darryl Veitch for helpful discussions. We thank the authors of QCircuit (\texttt{\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}}) for providing this very helpful package. P.P.R is funded by an ARC Future Fellowship (project FT160100397). We thank almost unethical quantities of 1,3,7-Trimethylxanthine for aiding in the motivation for this work.

>>>>

\begin{itemize}
\item We acknowledge Gavin Brennen, Joseph Clark, Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Jonathan Olson, Samuel Marks \& Darryl Veitch for helpful discussions.
\item We thank the authors of QCircuit (\texttt{\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}}) for providing this very helpful package.
\item P.P.R is funded by an ARC Future Fellowship (project FT160100397).
\item T.B is supported by the Shanghai Research Challenge Fund; New York University Global Seed Grants for Collaborative Research; National Natural Science Foundation of China (Grant No. 61571301); the Thousand Talents Program for Distinguished Young Scholars (Grant No. D1210036A); and the NSFC Research Fund for International Young Scientists (Grant No. 11650110425); NYU-ECNU Institute of Physics at NYU Shanghai; and the Science \& Technology Commission of Shanghai Municipality (Grant No. 17ZR1443600).
\item J.P.D would like to acknowledge support from the US Air Force Office of Scientific Research, the Army Research Office, the National Science Foundation, and the Northrop-Grumman Corporation.
\item We thank almost unethical quantities of 1,3,7-Trimethylxanthine\index{Caffeine} for aiding in the motivation for this work.
\end{enumerate}

### 2018-08-22 Sections/statement_of_contributions.tex
master text from Tim Byrnes - not edited in
Finished economics table
acks

P.P.R conceived and directed this project, developed the original ideas, and prepared most of the manuscript. Z.E.S and H.L.H prepared Sec.~\ref{sec:state_of_the_art}. W.J.M prepared Sec.~\ref{sec:rep_net}. S.I.M contributed to Sec.~\ref{sec:classical_nets}. R.L.M contributed to Sec.~\ref{sec:protocols_quant_int}. All authors played active roles in the discussions that developed this work.

>>>>

\begin{itemize}
\item P.P.R conceived and directed this project, developed the original ideas, and prepared most of the manuscript.
\item Z.E.S \& H.L.H prepared Sec.~\ref{sec:state_of_the_art}.
\item W.J.M prepared Sec.~\ref{sec:rep_net}. 
\item R.L.M contributed to Sec.~\ref{sec:protocols_quant_int}.
\item T.B \& J.P.D wrote Sec.~\ref{sec:quant_space_race}.
\item Z.H contributed to Secs.~\ref{sec:cryptowars}, \ref{sec:CV_QC}
\item C.F \& N.L wrote Sec.~\ref{sec:quantum_mind}.
\item N.L wrote Sec.~\ref{sec:verification}.
\item All authors played active roles in the discussions that developed this work. 
\end{itemize}

\comment{Add everyone else}
